---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

#### Add a project state badge 
See https://github.com/BCDevExchange/Our-Project-Docs/blob/master/discussion/projectstates.md
If you have bcgovr installed and you use RStudio, click the 'Insert BCDevex Badge' Addin.

# package name

Description of package

### Features

### Installation

### Usage

### Project Status

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/<pkg-name>/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

Apache 2.0 See our [license](LICENSE) for more details.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
