---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

<!-- Add a project state badge
See https://github.com/BCDevExchange/Our-Project-Docs/blob/master/discussion/projectstates.md
If you have bcgovr installed and you use RStudio, click the 'Insert BCDevex Badge' Addin. -->

# {{project_name}}

### Usage

Describe data being used (links), and how to run. Eg:

There are four core scripts that are required for the analysis, they need to be run in order:

- 01_clean.R
- 02_analysis.R
- 03_visualize.R
- 04_output.R

#### Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### Project Status

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/{{project_name}}/issues/).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
{{licence_text}}
```
